Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-03-09 sas2015/content/example.tex
squishing

In our example, the control flow within each method is straightforward and
all interesting issues arise from interprocedural control flow. In particular,
since the variable \code{a} may point to either an \code{A}-object or a \code{B}-object, 
the call on line~\ref{line:callfoo} may dispatch to either \code{A.foo()} or to \code{B.foo()},
and this is reflected by edges  
  from the node labeled $\highlight{\code{call}_\code{foo}}{greyblue}$ to the nodes labeled
  $\highlight{\code{start}_\code{A.foo()}}{bisque}$ and $\highlight{\code{start}_\code{B.foo()}}{lightsalmonpink}$
and by edges
  from the nodes labeled $\highlight{\code{end}_\code{A.foo}}{bisque}$ and $\highlight{\code{end}_\code{B.foo}}{lightsalmonpink}$ 
  to the node labeled  $\highlight{\code{return}_\code{foo}}{greyblue}$.  
Similarly, there are edges from the node labeled $\highlight{\code{call}_\code{bar}}{greyblue}$ to the nodes 
$\highlight{\code{start}_\code{A.bar()}}{bisque}$ and $\highlight{\code{start}_\code{B.bar()}}{lightsalmonpink}$, and 
edges
  from the nodes labeled $\highlight{\code{end}_\code{A.bar}}{bisque}$ and $\highlight{\code{end}_\code{B.bar}}{lightsalmonpink}$ 
  to the node labeled  $\highlight{\code{return}_\code{bar}}{greyblue}$.

>>>>

In our example, the control flow within each method is straightforward and
all interesting issues arise from interprocedural control flow. In particular,
since  \code{a} may point to either an \code{A}-object or a \code{B}-object, 
the call on line~\ref{line:callfoo} may dispatch to either \code{A.foo()} or to \code{B.foo()},
as is reflected by edges  
  from the node labeled $\highlight{\code{call}_\code{foo}}{greyblue}$ to the nodes labeled
  $\highlight{\code{start}_\code{A.foo()}}{bisque}$ and $\highlight{\code{start}_\code{B.foo()}}{lightsalmonpink}$
and by edges
  from the nodes labeled $\highlight{\code{end}_\code{A.foo}}{bisque}$ and $\highlight{\code{end}_\code{B.foo}}{lightsalmonpink}$ 
  to the node labeled  $\highlight{\code{return}_\code{foo}}{greyblue}$.  
Similarly, there are edges from the node labeled $\highlight{\code{call}_\code{bar}}{greyblue}$ to the nodes 
$\highlight{\code{start}_\code{A.bar()}}{bisque}$ and $\highlight{\code{start}_\code{B.bar()}}{lightsalmonpink}$, and 
edges
  from the nodes labeled $\highlight{\code{end}_\code{A.bar}}{bisque}$ and $\highlight{\code{end}_\code{B.bar}}{lightsalmonpink}$ 
  to the node labeled  $\highlight{\code{return}_\code{bar}}{greyblue}$.
